---
title: "Methylation"
author: "Bruna Oriol"
date: "6/4/2020"
output: html_document
---

# 1. Methylation Analysis of EPIC Array
```{r, message=FALSE, warning=FALSE}
rm(list=ls())

#Need to load libraries
library(minfi)
library(minfiData)
library(ChAMP)
library(reshape)
library(ggplot2)
library(lumi)
library(limma)
library(dplyr)
library(dendextend)
library(gplots)
library(RColorBrewer)
library(IlluminaHumanMethylationEPICanno.ilm10b2.hg19)
library(gtools)
library(sva)
library(MASS)
library(ggplot2)
library(ggrepel)
library(dendextend)
library(mixOmics)
library(FactoMineR)
library(factoextra)

```

## 2.1.Read 450K Data 
```{r, eval = FALSE}
# Annotation
annEPIC<-getAnnotation(IlluminaHumanMethylationEPICanno.ilm10b2.hg19)
annEPIC <- as.data.frame(annEPIC)

write.table(annEPIC, file = "../Meth/AnalysisEPIC/annotEPIC.txt" )
```


```{r, eval=FALSE}
#Read EPIC microarray intensity files
# myLoadEPIC <- champ.load(directory = "../../BCN02_Omics_paper/Meth/EPIC", methValue = "B", method = "minfi", filterXY = FALSE)
# RGSetEPIC <- myLoadEPIC$rgSet # Contains the raw intensities in the green and red channels.
# MSetEPIC <- myLoadEPIC$mset # Contains the methylated and unmethylated signals
# PDataEPIC <- myLoadEPIC$pd # Contains the arraZy associated metadata
```

```{r}

#Save the different objects.
#save(myLoadEPIC, RGSetEPIC, MSetEPIC, PDataEPIC, file = "../Meth/AnalysisEPIC/RData/myLoadEPIC.RData")

load("../Meth/AnalysisEPIC/RData/myLoadEPIC.RData")
```



```{r}

pd <- pData(RGSetEPIC) # Get the array associated metadata and convert it to data frame. 
Pheno <- data.frame(pd) 
dim(Pheno) #42 x 10 : 10 columns with array metadata. This is information from the sample sheet. 

### QC Report with Minfi
qcReport(RGSetEPIC, pdf = "../Meth/AnalysisEPIC/QCPlots/QC_EPIC.pdf")

### Read Phenotype Data: this is information we provide. 

PhenoEPIC <- read.csv(file = "../Meth/Info/targetsEPIC.csv") 
#Colnames:
  ##Sample name:The name of the DNA Sample (1,2,3, etc.)
  ## Ind_time: Individual + week ifnormation
  ## Individual: There are 15 individuals A02, etc.
  ## Week: Different timepoints: w0, w1, w6, w10.
  ## Rebound: Early/Late rebound


```


##2.2. Get Raw Beta values for methylation

```{r}

#Make sure there is the samer order in both df
int <- intersect(Pheno$Sample_Name, PhenoEPIC$Sample_Name)
PhenoEPIC <- PhenoEPIC[match(int, PhenoEPIC$Sample_Name),]

#Change rownames: put it as A02.w0, etc.
rownames(PhenoEPIC) <- paste(as.character(PhenoEPIC$Individual), as.character(PhenoEPIC$Week), sep = ".")
rownames(Pheno) <- rownames(PhenoEPIC)

Pheno <- cbind(Pheno, PhenoEPIC[,c(2,3,4,5,6)])
write.table(Pheno, file = "../Meth/AnalysisEPIC/PhenoEPIC.txt", sep = "\t", quote = F)

#Get Betas
RGSet.names <- data.frame(colnames(RGSetEPIC), Pheno$Sample_Name )
colnames(RGSetEPIC) <- rownames(Pheno)
df <- data.frame(colnames(RGSetEPIC), rownames(Pheno)) # verify same order

##Raw Betas
Beta.raw <- getBeta(RGSetEPIC)
colnames(Beta.raw)
write.table(Beta.raw, file = "../Meth/AnalysisEPIC/RawBeta.txt")
```



### 2.2.1 Exploratory Data Analysis - Raw Data
```{r}
rm(list = ls())


Beta.raw <- read.table("../Meth/AnalysisEPIC/RawBeta.txt")
Pheno <- read.delim("../Meth/AnalysisEPIC/PhenoEPIC.txt")

#MDS Raw Data
d <- dist(t(Beta.raw)) # euclidean distances between the rows (samples)
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )


#Make groups according week

df_fit$groups <- Pheno$Week

#Define plot theme
theme_MDS <- theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.text.x=element_text(colour="black"),
             axis.text.y=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"))

p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS  + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 2") + ylab("Coordinate 3")



#According rebound
unique(df_fit$Name)
groups <- rownames(df_fit)
Early <- grep("A12|A14|B06|A04|A13|A15|B05|B10|B14", groups)
Late <- grep("A02|A05|A09|B13", groups)
B03 <- grep("B03", groups)
B07 <- grep("B07", groups)


groups[Early] <- "Early"
groups[Late] <- "Late"
groups[B03] <- "B03"
groups[B07] <- "B07"


df_fit$groups <- groups
df_fit$groups <- factor(df_fit$groups, levels = c("Early", "Late", "B03", "B07"))




p <-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 2") + ylab("Coordinate 3")



#Hospital
df_fit$groups <- Pheno$Hospital

p <-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 2") + ylab("Coordinate 3")


```


```{r}

# Remove the Only woman of the study and make the plots again:

Beta.raw2 <- Beta.raw[, -grep("A14",colnames(Beta.raw))]
Pheno2 <- Pheno[-grep("A14",rownames(Pheno)),]


#MDS Raw Data

d <- dist(t(Beta.raw2)) # euclidean distances between the rows
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )


#According week
groups <- Pheno2$Week


df_fit$groups <- groups
df_fit$groups <- factor(df_fit$groups, levels = c("preCART", "MAP", "w24"))


p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS  + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 2") + ylab("Coordinate 3")



#According rebound
unique(df_fit$Name)
groups <- rownames(df_fit)
Early <- grep("A12|A14|B06|A04|A13|A15|B05|B10|B14", groups)
Late <- grep("A02|A05|A09|B13", groups)
B07 <-  grep("B07", groups)
B03 <- grep("B03", groups)


groups[Early] <- "Early"
groups[Late] <- "Late"
groups[B03] <- "B03"
groups[B07] <- "B07"


df_fit$groups <- groups
df_fit$groups <- factor(df_fit$groups, levels = c("Early", "Late", "B03", "B07"))


p <-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+ theme_MDS + xlab("Coordinate 2") + ylab("Coordinate 3")


```

### Estimate cell counts
```{r}
rm(list = ls())
load("../Meth/AnalysisEPIC/RData/myLoadEPIC.RData")
Pheno <- read.delim("../Meth/AnalysisEPIC/PhenoEPIC.txt")
Pheno2 <- Pheno[-grep("A14",rownames(Pheno)),] # remove the woman
WBCest <- estimateCellCounts(RGSetEPIC)
WBCest.df  <- as.data.frame(WBCest)
setdiff(rownames(WBCest.df), Pheno$Sample_Name)
rownames(WBCest.df ) <- rownames(Pheno)
Pheno.WBCEst <- cbind(Pheno, WBCest.df)
write.table(Pheno.WBCEst , "../Meth/AnalysisEPIC/PhenoWBCest.txt")
Pheno.WBCEst.EvsL <- Pheno.WBCEst[-grep("A14|B03|B07", rownames(Pheno.WBCEst)),]
write.table(Pheno.WBCEst.EvsL , "../Meth/AnalysisEPIC/PhenoWBCest_EvsL.txt")


```


## 2.3 Normalization - Quantile Normalization

```{r}
rm(list = ls())

Pheno <- read.delim("../Meth/AnalysisEPIC/PhenoEPIC.txt")
PhenoWBCest <- read.table("../Meth/AnalysisEPIC/PhenoWBCest.txt")

Pheno2 <- Pheno[-grep("A14",rownames(Pheno)),] # remove the woman
load("../Meth/AnalysisEPIC/RData/myLoadEPIC.RData")

#Remove the only woman of the study to avoid sex confounding.
colnames(RGSetEPIC) <- Pheno$Ind_time # change the name to A02.w0,etc.
dim(RGSetEPIC)
RGSetEPIC.1 <- RGSetEPIC[,-grep("A14", colnames(RGSetEPIC))]
dim(RGSetEPIC.1)

Pheno2$Ind_time <- factor(Pheno2$Ind_time, levels = unique(as.character(Pheno$Ind_time)))
Pheno2$Individual <- factor(Pheno2$Individual, levels = unique(as.character(Pheno$Individual)))

  
#Normalization (Quantile Norm)
Betas.QN.GenomicRS <- preprocessQuantile(RGSetEPIC.1)
Betas.QN <- getBeta(Betas.QN.GenomicRS)

write.table(Betas.QN, file = "../Meth/AnalysisEPIC/BetasQN.txt")

```

```{r}
#Exploratory analysis normalized data.
#Correlation with cell type

PCA.BetasQN <- prcomp(t(Betas.QN))
PCAs_1_15 <- PCA.BetasQN$x[,seq(1,15)]
phenotype <- PhenoWBCest[,seq(11,21)]
phenotype$Hospital <- factor(phenotype$Hospital, levels = c("HC","HUGTIP"), labels = c(0,1))
phenotype$Rebound <- factor(phenotype$Rebound, levels = c("Fast","Late"), labels = c(0,1))
phenotype.1 <- phenotype[, seq(6, 11)]
dim(PhenoWBCest)
dim(phenotype.1)
phenotype.1 <- phenotype.1[-grep("A14", phenotype$Individual),]


PCAs_1_15.preCART <- PCAs_1_15[grep("preCART", rownames(PCAs_1_15)),]
pheno.preCART <- phenotype.1[grep("preCART", rownames(PCAs_1_15)),]
cor.vector <- NULL
app.preCART <- apply(PCAs_1_15.preCART, 2, function(x){
  for (i in 1:ncol(pheno.preCART)){
    covariate <- pheno.preCART[,i]
    c <- cor(x = x, y = covariate, method = "spearman")
    cor.vector <- c(cor.vector,c)
    
  }
  return(cor.vector)
})
cor_df.preCART <- data.frame(app.preCART)
rownames(cor_df.preCART) <- colnames(pheno.preCART)
cor_df.preCART
cor_df.preCART.1 <- abs(cor_df.preCART)

library(pheatmap)
pheatmap(cor_df.preCART.1, cluster_rows = FALSE, cluster_cols = FALSE, 
         breaks = seq(0,1,0.1), 
         color = colorRampPalette(c("blue", "red"))(10), filename = "../Meth/AnalysisEPIC/QCPlots/PCAsPheatmap_preCART_today.pdf")






PCAs_1_15.MAP <- PCAs_1_15[grep("MAP", rownames(PCAs_1_15)),]
pheno.MAP <- phenotype.1[grep("MAP", rownames(PCAs_1_15)),]
cor.vector <- NULL
app.MAP <- apply(PCAs_1_15.MAP, 2, function(x){
  for (i in 1:ncol(pheno.MAP)){
    covariate <- pheno.MAP[,i]
    c <- cor(x = x, y = covariate, method = "spearman")
    cor.vector <- c(cor.vector, c)
    
  }
  return(cor.vector)
})
cor_df.MAP <- data.frame(app.MAP)
rownames(cor_df.MAP) <- colnames(pheno.MAP)
cor_df.MAP
cor_df.MAP.1 <- abs(cor_df.MAP)

library(pheatmap)
pheatmap(cor_df.MAP.1, cluster_rows = FALSE, cluster_cols = FALSE, 
         breaks = seq(0,1,0.1), 
         color = colorRampPalette(c("blue", "red"))(10), filename = "../Meth/AnalysisEPIC/QCPlots/PCAsPheatmap_MAP_today.pdf")





PCAs_1_15.w24 <- PCAs_1_15[grep("w24", rownames(PCAs_1_15)),]
pheno.w24 <- phenotype.1[grep("w24", rownames(PCAs_1_15)),]
cor.vector <- NULL
app.w24 <- apply(PCAs_1_15.w24, 2, function(x){
  for (i in 1:ncol(pheno.w24)){
    covariate <- pheno.w24[,i]
    c <- cor(x = x, y = covariate, method = "spearman")
    cor.vector <- c(cor.vector, c)
    
  }
  return(cor.vector)
})
cor_df.w24 <- data.frame(app.w24)
rownames(cor_df.w24) <- colnames(pheno.w24)
cor_df.w24
cor_df.w24.1 <- abs(cor_df.w24)

library(pheatmap)
pheatmap(cor_df.w24.1, cluster_rows = FALSE, cluster_cols = FALSE, 
         breaks = seq(0,1,0.1), 
         color = colorRampPalette(c("blue", "red"))(10), filename = "../Meth/AnalysisEPIC/QCPlots/PCAsPheatmap_w24_today.pdf")




#Boxplot per week
PhenoWBCest$Week <- factor(PhenoWBCest$Week, levels = c("preCART", "MAP", "w24"))
boxplot(CD8T ~ Week, PhenoWBCest)
kruskal.test(CD8T ~ Week, PhenoWBCest) #ns
boxplot(CD4T ~ Week, PhenoWBCest)
kruskal.test(CD4T ~ Week, PhenoWBCest)#ns
boxplot(NK ~ Week, PhenoWBCest)
kruskal.test(NK ~ Week, PhenoWBCest)#ns
boxplot(Bcell ~ Week, PhenoWBCest)
kruskal.test(Bcell ~ Week, PhenoWBCest)#ns
boxplot(Mono ~ Week, PhenoWBCest)
kruskal.test(Mono ~ Week, PhenoWBCest)#ns
boxplot(Gran ~ Week, PhenoWBCest)
kruskal.test(Gran~ Week, PhenoWBCest)#ns


#Reb

Pheno.WBCEst.EvsL <-PhenoWBCest[-grep("B03|B07|A14", PhenoWBCest$Individual),]
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = CD8T, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = CD4T, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = NK, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = Bcell, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = Mono, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")
p <- ggplot(Pheno.WBCEst.EvsL, aes(x=Week, y = Gran, fill = Rebound))
p + geom_boxplot(outlier.color = "transparent")



Pheno.preCART <- subset(Pheno.WBCEst.EvsL, Pheno.WBCEst.EvsL$Week == "preCART") #ns
wilcox.test(CD8T ~ Rebound, Pheno.preCART)  
wilcox.test(CD4T ~ Rebound, Pheno.preCART) 
wilcox.test(NK ~ Rebound, Pheno.preCART) 
wilcox.test(Bcell ~ Rebound, Pheno.preCART) 
wilcox.test(Mono ~ Rebound, Pheno.preCART) 
wilcox.test(Gran ~ Rebound, Pheno.preCART) 

Pheno.MAP <- subset(Pheno.WBCEst.EvsL, Pheno.WBCEst.EvsL$Week == "MAP") #ns
wilcox.test(CD8T ~ Rebound, Pheno.MAP) 
wilcox.test(CD4T ~ Rebound, Pheno.MAP) 
wilcox.test(NK ~ Rebound, Pheno.MAP) 
wilcox.test(Bcell ~ Rebound, Pheno.MAP) 
wilcox.test(Mono ~ Rebound, Pheno.MAP) 
wilcox.test(Gran ~ Rebound, Pheno.MAP) 


Pheno.w24 <- subset(Pheno.WBCEst.EvsL, Pheno.WBCEst.EvsL$Week == "w24") #ns
wilcox.test(CD8T ~ Rebound, Pheno.w24) 
wilcox.test(CD4T ~ Rebound, Pheno.w24) 
wilcox.test(NK ~ Rebound, Pheno.w24) 
wilcox.test(Bcell ~ Rebound, Pheno.w24) 
wilcox.test(Mono ~ Rebound, Pheno.w24) 
wilcox.test(Gran ~ Rebound, Pheno.w24) 



```

###2.3.1 Exploratory Analysis 

#### Density Plots

```{r}

densityPlot(as.matrix(Betas.QN), Pheno2$Rebound )
colourCount = length(unique(Pheno2$Individual))
getPalette = colorRampPalette(brewer.pal(8, "Dark2"))
densityPlot(as.matrix(Betas.QN), Pheno2$Individual , pal = getPalette(colourCount))
densityPlot(as.matrix(Betas.QN), Pheno2$Week )
densityPlot(as.matrix(Betas.QN), Pheno2$Slide )
densityPlot(as.matrix(Betas.QN), Pheno2$Hospital)

```

#### Boxplots

```{r}

boxplot(Betas.QN, main = "Betas QN", las = 2, cex = 0.5)

```

#### MDS
```{r}

#MDS NORMALIZED (Beta Quantiles) data

d <- dist(t(Betas.QN)) # euclidean distances between the rows
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )


#According week
df_fit$groups <- Pheno2$Week
df_fit$groups <- factor(df_fit$groups, levels = c("preCART", "MAP", "w24"))

#Define plot theme
theme <- theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.text.x=element_text(colour="black"),
             axis.text.y=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"))



p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 2")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 3")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= Name ))
p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 2") + ylab("Coordinate 3")


#According rebound
unique(df_fit$Name)
groups <- rownames(df_fit)
Early <- grep("A12|A14|B06|A04|A13|A15|B05|B10|B14", groups)
Late <- grep("A02|A05|A09|B13", groups)
B03 <- grep("B03", groups)
B07 <- grep("B07", groups)


groups[Early] <- "Early"
groups[Late] <- "Late"
groups[B03] <- "B03"
groups[B07] <- "B07"


df_fit$groups <- groups
df_fit$groups <- factor(df_fit$groups, levels = c("Early", "Late", "B03", "B07"))



p <- ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p + geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 2")

p <- ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p + geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 3")

p <- ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )))
p + geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 2") + ylab("Coordinate 3")


```

#### MDS QN per weeks (Evaluate Reb)
```{r}
rm(list = ls())
dir.create("../Meth/AnalysisEPIC/QCPlots/week_individually")
Bval.QN <- read.table("../Meth/AnalysisEPIC/BetasQN.txt") 
dim(Bval.QN) #485512     56


Pheno <- read.delim("../Meth/AnalysisEPIC/PhenoEPIC.txt")
Pheno2 <- Pheno[-grep("A14",rownames(Pheno)),]


Pheno2$Rebound <- factor(Pheno2$Rebound, levels = c("Fast", "Late", "Out"))
Pheno2[which(Pheno2$Individual == "B03"),]$Rebound <- "Out"


Bval.QN.preCART <- Bval.QN[, grep("preCART", colnames(Bval.QN))]
Bval.QN.MAP <- Bval.QN[, grep("MAP", colnames(Bval.QN))]
Bval.QN.w24 <- Bval.QN[, grep("w24", colnames(Bval.QN))]

Pheno2.preCART <- Pheno2[grep("preCART", Pheno2$Week), ]
Pheno2.MAP <- Pheno2[grep("MAP", Pheno2$Week), ]
Pheno2.w24 <- Pheno2[grep("w24", Pheno2$Week), ]

#Define plot theme
theme <- theme(panel.background = element_blank(),
             panel.border=element_rect(fill=NA),
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             strip.background=element_blank(),
             axis.text.x=element_text(colour="black"),
             axis.text.y=element_text(colour="black"),
             axis.ticks=element_line(colour="black"),
             plot.margin=unit(c(1,1,1,1),"line"))



#preCART
d <- dist(t(Bval.QN.preCART)) # euclidean distances between the rows
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )
df_fit$groups <- Pheno2.preCART$Rebound

p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 2")
p + stat_ellipse() + ggtitle("preCART")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("preCART")


p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 2") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("preCART")




#MAP

d <- dist(t(Bval.QN.MAP)) # euclidean distances between the rows
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )
df_fit$groups <- Pheno2.MAP$Rebound

p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 2")
p + stat_ellipse() + ggtitle("MAP")


p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("MAP")


p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 2") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("MAP")


#w24
d <- dist(t(Bval.QN.w24)) # euclidean distances betw24een the row24s
fit <- cmdscale(d,eig=TRUE, k=4) # k is the number of dim

df_fit <- data.frame(fit$points) 
df_fit$Name <- sapply(strsplit(rownames(df_fit), "[.]"), function(x) x[1] )
df_fit$groups <- Pheno2.w24$Rebound

p<-ggplot(df_fit ,aes(x=X1,y=X2,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 2")
p + stat_ellipse() + ggtitle("w24")

p<-ggplot(df_fit ,aes(x=X1,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 1") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("w24")

p<-ggplot(df_fit ,aes(x=X2,y=X3,color=groups, label= Name))
p<-p+geom_point() + geom_text_repel(aes(label=Name), size =3)+theme + xlab("Coordinate 2") + ylab("Coordinate 3")
p + stat_ellipse() + ggtitle("w24")


```

###2.3.3 Non-specific Filtering
In this case we take the proves at percential 0.75, therefore the 25% of most variables probes. 

```{r}
# M with more variable pos.
rm(list = ls())
Bval.QN <- read.table("../Meth/AnalysisEPIC/BetasQN.txt") 
dim(Bval.QN) #865859     30
Mval.QN <- beta2m(Bval.QN)

sd <- apply(Mval.QN, 1, sd)
plot(density(sd, na.rm = T))
hist(sd)


sd.o <- sort(sd) #order sd increasing
sd.o_df <- data.frame(sd.o)
head(sd.o_df)
tail(sd.o_df)

# plot sd results tp decide cut-off. 
png("../Meth/AnalysisEPIC/QCPlots/sd_Combat.png", res = 300, width = 3, height =3, units = "in",   pointsize = 5)
plot(sd.o)
abline(h=quantile(sd.o, probs=0.25), col = "red")
abline(h=quantile(sd.o, probs=0.75), col = "blue")
abline(h=quantile(sd.o, probs=0.80), col = "orange")
abline(h=quantile(sd.o, probs=0.90), col = "yellow")
abline(h=quantile(sd.o, probs=0.95), col = "pink")
legend(100, 2.5, legend = c("P25", "P75", "P80", "P90", "P95"), col=c("red", "blue", "orange", "yellow", "pink"), lty =1)
dev.off()


CpGVariable <- sd.o[which(sd.o >quantile(sd.o, probs=0.75))]
length(CpGVariable) #216465
head(CpGVariable)


Mval.QN1 <- Mval.QN[names(CpGVariable),]
dim(Mval.QN) #485512     56
dim(Mval.QN1) # 121378     56
Bvalues.QN1 <- m2beta(Mval.QN1)

write.table(Mval.QN1, file = "../Meth/AnalysisEPIC/QNMval_sel.txt")
write.table(Bvalues.QN1, file = "../Meth/AnalysisEPIC/QNBetaval_sel.txt")


```

##3. Identify DMPs with Limma - Weeks

```{r}

dir.create("../Meth/AnalysisEPIC/OutputFiles")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks/LimmaBlock")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks/LimmaBlockAnnot")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks/LimmaBlockAnnot/adjpval")



rm(list = ls())

Mval.QN1 <- read.table("../Meth/AnalysisEPIC/QNMval_sel.txt")
Pheno <- read.delim("../Meth/AnalysisEPIC/PhenoEPIC.txt")
Pheno2 <- Pheno[-grep("A14",rownames(Pheno)),]
PhenoWBCEst <- read.table("../Meth/AnalysisEPIC/PhenoWBCest.txt")
PhenoWBCEst <- PhenoWBCEst[-grep("A14", rownames(PhenoWBCEst)),]
dim(Pheno2)
dim(PhenoWBCEst)


# Read annEPIC
annEPIC <- read.table("../Meth/AnalysisEPIC/annotEPIC.txt")

# Limma Model
Week <- factor(PhenoWBCEst$Week, levels = c("preCART", "MAP", "w24"))


mod1 <- model.matrix(~0 + Week)

colnames(mod1)=levels(Week)



contr.matrix_week_1 <- makeContrasts(
  
  MAPvspreCART = MAP - preCART,
  w24vspreCART = w24 - preCART,
  w24vsMAP = w24 - MAP,
  
  levels=colnames(mod1))

cor1 <- duplicateCorrelation(Mval.QN1,mod1,block=PhenoWBCEst$Individual)
fit=lmFit(Mval.QN1,mod1, block=PhenoWBCEst$Individual, correlation=cor1$consensus)


## SIMPLE COMPARISON
fit1=contrasts.fit(fit, contrasts=contr.matrix_week_1)
fit1.2=eBayes(fit1)
summary(decideTests(fit1.2))


#All CpGs
for (i in  colnames(fit1.2$coefficients)){
  toptable <-  topTable(fit1.2, coef=i, sort="p", n=Inf, adjust = "BH")
  write.table( toptable, paste(paste("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks/LimmaBlock/", i),".txt",sep=""),quote=F)
  toptable.annotated <- merge(toptable,annEPIC[,c("chr", "UCSC_RefGene_Name","Relation_to_Island","UCSC_RefGene_Group", "UCSC_RefGene_Accession",  "Probe_rs")],
                              by="row.names")
  toptable.annotated <-  subset(toptable.annotated, toptable.annotated$UCSC_RefGene_Name != "")
  write.table(toptable.annotated, paste(paste("../Meth/AnalysisEPIC/OutputFiles/DMPs_weeks/LimmaBlockAnnot/", i),".txt",sep=""),quote=F)
}


```

##2.5. Identify DMPs with Limma - Rebound (also in individual groups)
For this part we need to remove B03 and B07

```{r}

dir.create("../Meth/AnalysisEPIC/OutputFiles")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb/LimmaBlock")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb/LimmaBlockAnnot")
dir.create("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb/LimmaBlockAnnot/adjpval")

rm(list = ls())

Mval.QN1 <- read.table("../Meth/AnalysisEPIC/QNMval_sel.txt")
Mval.QN1 <- Mval.QN1[,-grep("B03",colnames(Mval.QN1))]

PhenoWBCEst <- read.table("../Meth/AnalysisEPIC/PhenoWBCest.txt")

PhenoWBCEst <- PhenoWBCEst[-grep("A14", rownames(PhenoWBCEst)),]
Pheno2 <- PhenoWBCEst [-grep("B03|A14",rownames(PhenoWBCEst)),]

df <- data.frame(rownames(Pheno2), colnames(Mval.QN1))

# Read annEPIC
annEPIC <- read.table("../Meth/AnalysisEPIC/annotEPIC.txt")

# Limma Model
Week_Rebound <- factor(paste(Pheno2$Week, Pheno2$Rebound, sep ="_"), levels = c("preCART_Late", "MAP_Late","w24_Late", 
                                                                              "preCART_Fast", "MAP_Fast", "w24_Fast"))

mod1 <- model.matrix(~0 + Week_Rebound)
colnames(mod1)=levels(Week_Rebound)

contr.matrix_rb1 <- makeContrasts(
  
  preCART_FastvsLate = preCART_Fast-preCART_Late,
  MAP_FastvsLate =  MAP_Fast-MAP_Late,
  w24_FastvsLate =  w24_Fast-w24_Late,

  
  FastvsLate = ((preCART_Fast+MAP_Fast+w24_Fast)/3) - ((preCART_Late+MAP_Late+w24_Late)/3),

  levels=colnames(mod1))



fit=lmFit(Mval.QN1,mod1)


## SIMPLE COMPARISON
fit1=contrasts.fit(fit, contrasts=contr.matrix_rb1)
fit1.2=eBayes(fit1)
summary(decideTests(fit1.2))


#All CpGs
for (i in  colnames(fit1.2$coefficients)){
  toptable <-  topTable(fit1.2, coef=i, sort="p", n=Inf, adjust = "BH")
  write.table( toptable, paste(paste("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb/LimmaBlock/", i),".txt",sep=""),quote=F)
  toptable.annotated <- merge(toptable,annEPIC[,c("chr", "UCSC_RefGene_Name","Relation_to_Island","UCSC_RefGene_Group", "UCSC_RefGene_Accession",  "Probe_rs")],
                              by="row.names")
  toptable.annotated <-  subset(toptable.annotated, toptable.annotated$UCSC_RefGene_Name != "")
  write.table(toptable.annotated, paste(paste("../Meth/AnalysisEPIC/OutputFiles/DMPs_rb/LimmaBlockAnnot/", i),".txt",sep=""),quote=F)
}

```














